---
output:
  github_document:
    toc: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# R and Lego

Repo holds photos that depict R data structures and operations via Lego.

These images are released under a [Creative Commons Attribution 4.0 International License](https://creativecommons.org/licenses/by/4.0/).

# Gallery of the photos

Clickable gallery, which is created from a small chunk of R code in an executable R Markdown [`README.Rmd`](README.Rmd). [This gist](https://gist.github.com/jennybc/0239f65633e09df7e5f4) shows similar syntax but with markdown image links, instead of html.

```{r make-smaller-pngs, include = FALSE}
library(purrr)
fig_files <- list.files(pattern = "lego-rstats.*\\.jpg$")
smaller_files <- list.files(pattern = "smaller")
fig_files <- setdiff(fig_files, smaller_files)
fig_files_smaller <- gsub("(^.*)(\\.jpg$)", "\\1-smaller\\2", fig_files)

## make sure all PNGs exist in a 'smaller' version
fig_files_needed <- !file.exists(fig_files_smaller)
if (any(fig_files_needed)) {
  library(magick)
  figs <- map(fig_files[fig_files_needed], image_read)
  figs %>% 
    map(image_scale, geometry = "400") %>% 
    map2(fig_files_smaller[fig_files_needed], image_write)
}
fig_files_smaller <- gsub("(^.*)(\\.jpg$)", "\\1-smaller\\2", fig_files)  
```

```{r make-gallery, results = "asis", echo = FALSE}
## the real business is here
tags <- sprintf("<a href=\"%s\"><img src=\"%s\"></a>",
                fig_files, fig_files_smaller)
cat(tags)
```

### Notes

Photos added in waves and file name/number is roughly chronological. At least I think so.

  * 2016-10-23 just playing around, 1st two photos of the large plate
  * 2016-11-06 first big wave
  * 2016-11-06 redo pants photo due to 2 vs 3 peg gap (wtf?)
  * 2016-11-15 have learned alot from first wave
    - BOUGHT A TRIPOD
    - retake photos of nested data frame, since david smith discovered a missing lego :scream:
    - made photos more suitable for map, map2, pmap, map_df
    - illustrate NAs in atomic vector
    - photograph atomic vectors on contrasting construction paper so keynote alpha transparency works
  * TO DOs:
    - retake antenna photo
    - map_SOMETHING when elements aren't valid ... safely?
    - horizontal hair-only (like the weapons)
    - columnar white background bald minis, hair, minis w/ hair
    - each mini, fully decked out, alone, ready for alpha transparency
  
